\documentclass[journal]{IEEEtran}

\usepackage{amsmath}
\usepackage{pifont}
\usepackage{url}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

\begin{document}

\title {DemoFL: Democratic Federated Learning Based on Multi-party Computation and Consensus Algorithm}

\author{Zhaoyang~Han, 
        Chunpeng~Ge, 
        Zhe~Liu$^*$, 
        and~Chuan~Ma%
\thanks{Zhaoyang~Han, Chunpeng~Ge, and~Zhe~Liu are with the College of Computer Science and Technology, Nanjing University of Aeronautics and Astronautics, Nanjing, 210016, China (e-mail: nuaahanzy@gmail.com; gecp@nuaa.edu.cn; sduliuzhe@gmail.com).}

\thanks{Chuan~Ma is with the School of Electrical and Optical Engineering, Nanjing University of Science and Technology, Nanjing 210094, China (e-mail: chuan.ma@njust.edu.cn).

$^*$Corresponding author: Zhe~Liu.}
}

\maketitle

\begin{abstract}
Federated Learning (FL) is a framework based on which numerous parties can train a machine learning model cooperatively without leaking information about their data. However, attackers can reconstruct FL parties' data through the leaked parameters. Therefore, secure aggregation is critical to ensure privacy-preserving in FL frameworks. The current secure aggregation algorithms in FL rely on the parties to establish a secure channel between each other, which leads to a heavy communication overhead. Moreover, establishing secure channels between parties in FL may be unrealistic in some scenarios.

In this paper, we propose Democratic Federated Learning (DemoFL), which is a privacy-preserving FL framework based on secure multi-party computation (MPC) and simplified consensus algorithms. Our method adopts secret sharing to hide local model parameters, and runs a consensus algorithm to ensure that the communication is reliable and robust. DemoFL utilizes a hierarchical structure to reduce the complexity from $O(n^2)$ to approximatively $O(n)$, and it realizes high security and robustness without reducing accuracy. We also conducted a performance evaluation to demonstrate the practicality and efficiency of our proposed framework. 

\end{abstract}

\begin{IEEEkeywords}
    Federated Learning, Secure Aggregation, Machine Learning, Multi-party Computation, Consensus algorithm
\end{IEEEkeywords}


\section{Introduction} 
\label{sec:intro}
\input{sec/intro}

\section{Background}
\label{sec:back}
\input{sec/back}

\section{Related Work}
\label{sec:related}
\input{sec/related}

\section{Democratic Federated Learning}
\label{sec:DemoFL}
\input{sec/DemoFL}

\section{Efficiency and Security Evaluation}
\label{sec:eval}
\input{sec/eval}

\section{Experimental Results}
\label{sec:exp}
\input{sec/exp}

\section{Conclusion and Future Works}
\label{sec:conc}
\input{sec/conc}


\bibliography{main.bib}
\bibliographystyle{IEEEtran}
\end{document}