\documentclass[journal]{IEEEtran}

\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

\title {SOFL: Self-organizing Federated Learning Based on Multi-party Computation and Consensus Algorithm}
\author{Zhaoyang Han}


\begin{document}
\maketitle

\begin{abstract}
With the rapid development and widespread application of artificial intelligence (AI) technologies, privacy and security are attracting more attention in machine learning areas. Federated Learning (FL) is a framework based on which numerous parties can train a machine learning model cooperatively without leaking information about their data. Parties in FL send parameters of local models instead of their data to the server in order to obtain the global model securely. However, researches have proven that attackers can reveal FL parties' data through the leakage of local model parameters. Therefore, secure aggregation is requisite to ensure privacy-preserving in FL frameworks. Moreover, it usually costs a lot for FL parties to securely communicate with each other. Therefore, efficiency is another problem for FL to address. In this paper, we propose a privacy-preserving FL framework based on secure multi-party computation (MPC) and simplified consensus algorithm, namely Self-organizing Federated Learning (SOFL). Our method adopts secret sharing to hide local model parameters, and runs a consensus algorithm to ensure the communication is reliable, robust and efficient.

\end{abstract}

\begin{IEEEkeywords}
    Federated Learning, Secure Aggregation, Machine Learning, Multi-party Computation, Consensus algorithm
\end{IEEEkeywords}


\section{Introduction} 
\label{sec:intro}
\input{sec/intro}

\section{Background}
\label{sec:back}
\input{sec/back}

\section{Related Work}
\label{sec:related}
\input{sec/related}


\section{Self-organizing Federated Learning}
\label{sec:sofl}
\input{sec/sofl}


\section{Efficiency and Security Evaluation}
\label{sec:eval}
\input{sec/eval}


\section{Experimental Results}
\label{sec:exp}
\input{sec/exp}


\section{Conclusion and Future Works}
\label{sec:conc}
\input{sec/conc}



\bibliography{mpc.bib}
\bibliographystyle{IEEEtran}
\end{document}